Supplementary Information

### 2020-12-23 doc/manuscript/MEE_manuscript.Rmd
update manuscript

@@

![**Figure 4 | Growth sensitivity to DBH: (a) $RW$, (b) $BAI$, (c) $\Delta AGB$.** Relationships for species are plotted when included in the top model. Other terms in the model are held constant at their median. Best-fit polynomials are plotted with solid lines when both first- and second-order terms are significant (t-test’s p-value <0.05), DASHED lines when only one term is significant, and dotted lines when neither is significant.  Transparent ribbons indicate 95% confidence intervals.](tables_figures/DBH_responses.png)

>>>>

*(here, I want to frame presentation around light-tolerance and stand openness:)*

@@

![**Figure 4 | Growth sensitivity to DBH: (a) $RW$, (b) $BAI$, (c) $\Delta AGB$.** Relationships for species are plotted when included in the top model. Other terms in the model are held constant at their median. Best-fit polynomials are plotted with solid lines when both first- and second-order terms are significant (t-test’s p-value <0.05), dashed lines when only one term is significant, and dotted lines when neither is significant.  Transparent ribbons indicate 95% confidence intervals.](tables_figures/DBH_responses.png)
